David Wang
CSE15
Homework 5




In order to do the Diffie-Hellman Key Exchange, we first need two public keys, p and g.

In this case, p = 9433, and g = 5.

Then both people have to choose a private random number. You chose 'a', and I would have to choose 'b'.

With your private key 'a', you computed A = (g ^ a) mod p and gave the result, A = 1218, to me.

In exchange, I would use my private key 'b', and compute B = (g ^ b) mod p. And give that result B to you.

To calculate the common secret key, you would use my transmitted number B and calcalate  K = B^a mod p.

I would use your transmitted key A to calculate K = A^b mod p.

In the end, we should both end up with the same value for K.

1.) 

Since you gave me A = 1218, I would have to give you a value for B after choosing my secret key 'b' and calculating B = g^b mod p.

Then I would calculate the key using K = A^b mod p and you would calculate K using K = B^a mod p.

We should end up with the same K.

Assuming I chose the value b = 2, 

I would calculate K = A^b mod p to get the key.

K = (1218)^(2) mod 9433 = 2543

Since B = g^b mod p, using my value of 2

B = 5^2 mod 9433 = 25

For you to calculate the key,

K = B^a mod p

= 25^ a mod 9433

Since our values for K should be the same, we would need some value for a such that 25^a mod 9433 would also equal 2543.

2.)

If Trudy and Eve knew that p = 9433, g = 5 and your transmitted value of A = 1218 

They would have to figure out what your private key 'a' was such that 

A = 1218 = g^a mod P

B = g^b mod p 

B^a mod p = A^b mod p.

Assuming my value of b were 2,

they would just have to do K = A^b mod p

K = 1218^2 mod 9433

and get the result K = 2543.

Assuming I used b for mod p.

3.)

The value of your K would be different depending on what I chose for the value of b.

Assuming my private key 'b' was 2,

B = g^b mod p
= 5^2 mod 9433 = 25

I would give that value of 25 to you, and you would calculate K = 25^a mod 9433

a would have to be a value such that 

B^a mod 9433 = A^b mod 9433

Since I chose b = 2,

25^a mod 9433 = 1218^2 mod 9433

If I had  chosen differently, the B I transmitted to you would have been different. And since your K relies on B, it would have been different.

In order to calculate a itself,

we have A = g^a mod p

and we know A = 1218, g = 5 and p = 9433

1218 = 5^a mod 9433

Solve algebraically to find a.





